The Shape Matching Element Method for Meshless Animation of NURBs Models

### 2021-01-10 paper/sections/intro.tex

Our approach is an extension of the recently developed Virtual Element Method (VEM) for solving PDEs on domains tiled with arbitrary polygons.
We establish a connection between VEM and the well-known shape matching simulation algorithm  which enables us 
to derive equations of motion for an arbitrary NURBS model using Lagrangian Mechanics. 
Importantly, we show how to replace volumetric data structures for integration with ray casting approaches which enables
our meshless approach to isogeometric elastodynamic simulation of volumetric structures.

>>>>

Our approach is an extension of the recently developed Virtual Element Method (VEM) for solving PDEs on domains tiled with arbitrary polygons.
We establish a connection between VEM and the well-known shape matching simulation algorithm  which enables us 
to derive equations of motion for an arbitrary NURBS model using Lagrangian Mechanics. 
Importantly, we show how to replace volumetric data structures for integration with ray casting approaches which enables
our meshless approach to isogeometric elastodynamic physically-based animation of volumetric structures.
